Transparent Changes

### 2022-04-27 scripts/review.Rmd
Analyze extracted data

# Get final decisions
s_res_final <- read.csv("../data/screen/abstract_screening.csv")
# number excluded 
abstr_excl_count <- sum(!is.na(s_res_final$decision))
# extract remaining data
ft_screen <- sampled_data[is.na(s_res_final$decision), ]

@@

write.csv(extr, "../data/extract/extraction.csv", row.names = FALSE)```

>>>>

# Get final decisions
s_res_final <- read.csv("../data/screen/abstract_screening.csv")
# number excluded 
abstr_excl_count <- sum(!is.na(s_res_final$decision))
# reasons for exclusion
table(s_res_final$decision)
# extract remaining data
ft_screen <- sampled_data[is.na(s_res_final$decision), ]

@@

write.csv(extr, "../data/extract/extraction.csv", row.names = FALSE)
```

#### Read and clean extracted data

```{r clean, warning=FALSE}
ext <- read.csv("../data/extract/extraction.csv")

# Create column for processing type + averaging type combination
ext$proc_combination <- paste(ext$ptype, ext$averaging, sep = "-")
ext$proc_combination[ext$proc_combination == "NA-NA"] <- NA

# Separate parameter column for multiple parameters (i.e. multiple binned averages)
# and calculate total duration

split_parameters <- function(n) {
  value <- ext$parameters[n]
  if (grepl("x", value)) {
    value_split <- strsplit(value, "x")[[1]]
    out <- data.frame(
      param_times = as.numeric(value_split[1]), 
      param_value = as.numeric(value_split[2])
    )
    out$param_duration <- out$param_times * out$param_value
  } else {
    out <- data.frame(
      param_times = NA, 
      param_value = as.numeric(value), 
      param_duration = as.numeric(value)
    )
  }
  out
}

ext <- cbind(ext, purrr::map_dfr(seq_len(nrow(ext)), split_parameters))

# save data
# save(ext, file = "../data/review.Rda")

# Show metabolic carts used
table(ext$type, useNA = "ifany")
```

#### Analyze extracted data

```{r percentages}
load("../data/review.Rda")
# Remove Douglas bag measurements
ext <- ext[ext$type != "douglas", ]

n_total <- nrow(ext)
ext_bbb <- ext[ext$type == "bbb" & !is.na(ext$type),]
n_bbb <- nrow(ext_bbb)

# Type of metabolic cart
p_cart <- 1 - (sum(grepl("NA", ext$cart) | is.na(ext$cart)) / n_total)

# Preprocessing
p_pre <- sum(!is.na(ext_bbb$pre)) / n_bbb

# Software
p_software <- sum(!is.na(ext_bbb$software)) / n_bbb

# Processing strategy
p_proc <- sum(!is.na(ext$ptype) & !is.na(ext$averaging) & !is.na(ext$parameters)) / n_total

# Source
p_source <- sum(!is.na(ext$source)) / n_total

reporting <- data.frame(
  "cart" = p_cart,
  "pre" = p_pre,
  "software" = p_software,
  "processing" = p_proc,
  "source" = p_source
)

save(reporting, file = "../data/reporting.Rda")

knitr::kable(purrr::map_dfr(reporting, scales::percent, accuracy = 0.1))

```{r analysis}
# Show data processing strategies overall
table(ext$ptype, useNA = "ifany")

# Show data processing type for breath-by-breath measurements only
table(ext$proc_combination[ext$type == "bbb"], useNA = "ifany")

# Plot for total calculation interval lengths
ext[ext$ptype == "time" & !is.na(ext$ptype), ] |>
  ggplot(aes(y = param_duration)) +
    geom_bar() +
  geom_text(aes(label = ..count..), stat = "count", hjust = 1.2, colour = "white") +
    scale_y_reverse(
      breaks = c(5, 10, 15, 20, 30, 45, 60),
      minor_breaks = NULL,
      name = "Duration (s)"
    ) +
    scale_x_continuous(
      minor_breaks = NULL,
      name = "Count",
      breaks = c(0, 10, 20, 30, 40),
      labels = NULL,
      expand = c(0, 0),
      position = "top"
    ) +
    theme_minimal(13) +
   theme(
     panel.grid.major.y = element_blank(),
     axis.ticks.y = element_line(colour = "grey", size = 0.5)
    )

ggsave("../plots/duration_count.png", width = 5, height = 3, dpi = 600, bg = "white")
```

```{r}
library(treemapify)
library(dplyr)

ext_count <- ext |> 
  filter(type == "bbb") |>
  select(c(proc_combination, ptype)) |>
  filter(!is.na(proc_combination)) |>
  count(proc_combination, ptype)

ext_count$proc_combination <- factor(
  ext_count$proc_combination, 
  levels = c("breath-binned", "time-moving", "breath-moving", "time-binned", "time-mbinned"),
  labels = c("Binned Breath","Moving Time", "Moving Breath", "Binned Time", "Multiple Binned Time"))

percs <- scales::percent(ext_count$n / sum(ext_count$n))
ext_count$label <- paste0(ext_count$proc_combination, " (", percs, ")")
ext_count$subgroup <- c(1, 1, 2, 3, 4)

ggplot(ext_count, aes(area = n, fill = proc_combination, label = label, subgroup = subgroup)) +
  geom_treemap(show.legend = FALSE, start = "topleft") +
  geom_treemap_text(reflow = TRUE, place = "centre", start = "topleft")

ggsave("../plots/strategies.png", width = 5, height = 3, dpi = 600, bg = "white")
```
